\section{Introduction}

\subsection{Objectives}

The primary goal of this project is to analyze and design a CMOS Low Noise Amplifier (LNA) using 350~nm technology, with comparative analysis in more advanced nodes such as 65~nm and 45~nm. The designed LNA must meet key RF specifications: gain ($S_{21}$) greater than 10~dB, noise figure (NF) below 3~dB, and proper input/output impedance matching ($S_{11}$ and $S_{22}$ less than $-10$~dB). These requirements ensure signal integrity, noise reduction, and compatibility with standard 50~$\Omega$ systems. Validation of the design is carried out via simulations in LTSpice and Cadence, with results benchmarked against theoretical predictions.


In table \ref{tab:specifications}, the specifications for the LNA are summarized. The design will be validated through circuit simulations using LTSpice, and the results will be compared with theoretical expectations.

\begin{table}[h]
    \centering
    \caption{LNA Specifications}
    \begin{tabularx}{\textwidth}{
        >{\centering\arraybackslash}X 
        >{\centering\arraybackslash}X 
        }
        \toprule
        \textbf{Specification} & \textbf{Value}\\
        \midrule
        Gain (S21) & $> \SI{10}{\decibel}$  \\
        \midrule
        Noise Figure (NF) & $< \SI{3}{\decibel}$  \\
        \midrule
        Input Impedance (S11) & $< -\SI{10}{\decibel}$  \\
        \midrule
        Output Impedance (S22) & $< -\SI{10}{\decibel}$ \\
        \midrule
        Technology Node & \SI{350}{\nano\meter}, \SI{65}{\nano\meter}, \SI{45}{\nano\meter} \\
        \midrule
        Frequency (\SI{350}{\nano\meter}) & 0.1 \si{\giga \hertz} to 2 \si{\giga \hertz} \\
        \midrule
        Frequency (\SI{65}{\nano\meter}) & 5 \si{\giga \hertz} \\
        \midrule
        Frequency (\SI{45}{\nano\meter}) & 10 \si{\giga \hertz} \\
        \midrule
        VDD (\SI{350}{\nano\meter}, \SI{65}{\nano\meter}, \SI{45}{\nano\meter} ) & 2.5\si{\volt}, 1.2\si{\volt}, 1\si{\volt} \\
        \midrule
        K constant (\SI{350}{\nano\meter}, \SI{65}{\nano\meter}, \SI{45}{\nano\meter} ) & 200 \si{\micro{}}, 244.961 \si{\micro{}}, 50 \si{\micro{}} \\
        \midrule
        $L_{min}$ (\SI{350}{\nano\meter}, \SI{65}{\nano\meter}, \SI{45}{\nano\meter}) & 350 \si{\nano \meter}, 65 \si{\nano \meter}, 45 \si{\nano \meter} \\
        \midrule
        n ($g_m$ ratio) & 3 \\
        \bottomrule
    \end{tabularx}
    \label{tab:specifications}
\end{table}

\subsection{Motivation}

Modern telecommunication systems operate at high frequencies and data rates, and the LNA plays a critical role in the receiver chain, as it amplifies weak incoming signals while minimizing noise. A well-designed LNA ensures signal integrity, energy efficiency, and compliance with communication standards. This project gives students the opportunity to apply theoretical knowledge of analog and RF electronics by developing and validating a practical CMOS-based LNA using circuit simulation tools such as LTSpice.